method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
new way of assignment of blocks

data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
data_ER$block[data_ER$trigger == 21] <- "1_view_neu"

for (i in 1:nrow(data_ER)) {

  if (data_ER$trigger[i] == 21) {

    data_ER$block[i] = "view_neu"

  } else if (data_ER$trigger[i] == 22) {

    data_ER$block[i] = "view_neg"

  } else if (data_ER$trigger[i] == 23 ) {

    data_ER$block[i] = "distraction"

  } else if (data_ER$trigger[i] == 24 ) {

    data_ER$block[i] = "distancing"

  } else if (data_ER$trigge[i] == 25 ) {

    data_ER$block[i] = "suppression"

  } else if (data_ER$trigger[i] == 26) {

    data_ER$block[i] = "choice"
  }
}

>>>>

data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
data_ER$block[data_ER$trigger == 22] <- "2_view_neg"
data_ER$block[data_ER$trigger == 23] <- "3_distraction"
data_ER$block[data_ER$trigger == 24] <- "4_distancing"
data_ER$block[data_ER$trigger == 25] <- "5_suppression"
data_ER$block[data_ER$trigger == 26] <- "6_choice"
